\documentclass[twocolumn,prd,superscriptaddress,floatfix]{revtex4-2}

\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{xspace}
\newcommand{\FloatBarrier}{\clearpage}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}

% macros
\newcommand{\isr}{Inflationary Sector Renormalization\xspace}
\newcommand{\ISR}{ISR\xspace}
\newcommand{\kl}{KL\xspace}
\newcommand{\xzero}{$x_0$\xspace}
\newcommand{\lsim}{\mathrel{\mathchoice{\vcenter{\offinterlineskip
  \hbox{$\sim$}\vskip-0.5ex\hbox{$<$}}}{\vcenter{\offinterlineskip
  \hbox{$\sim$}\vskip-0.5ex\hbox{$<$}}}{\vcenter{\offinterlineskip
  \hbox{$\scriptstyle\sim$}\vskip-0.3ex\hbox{$\scriptstyle<$}}}
  {\vcenter{\offinterlineskip\hbox{$\scriptscriptstyle\sim$}
  \vskip-0.2ex\hbox{$\scriptscriptstyle<$}}}}}

\begin{document}

\title{Inflationary Sector Renormalization in a Stochastic Toy Landscape}

\author{Jake Enholm}

\date{\today}

\begin{abstract}
Eternal inflation motivates ensembles of causally disconnected or weakly related
inflationary domains, but extracting probabilities from such ensembles requires a
measure over an infinite or cutoff-dependent population.
We propose \isr (\ISR), a configuration-space locality-weighted sector framework in which
unobserved simulated sectors are conditionally reweighted within a finite stochastic ensemble.
Rather than treating all sectors as equally countable, \ISR weights sectors by
field-space proximity, basin structure, and local ancestry proxies.
We implement a stochastic toy landscape with multiple vacuum basins and compare
\ISR against a naive global census measure under increasing trajectory cutoffs.
The cutoff studied here is the trajectory-sampling cutoff (number of simulated
sectors), not a cosmological volume cutoff.
In a 10,000-trajectory run, the global census favors the most common basin, while
\ISR shifts weight toward the basin local to the observable patch and reduces
mean KL drift by approximately a factor of two in the physically meaningful
kernel regime.
Across 100 sigma-by-seed stress tests, \ISR improves final KL stability in 98
cases, with failures concentrated at broad initial-condition spread.
A simple shifted-well perturbation test suggests that the improvement is not
solely an artifact of the original well placement.
We also examine basin-boundary exceptions, kernel-weighted sector averaging under
unobserved-sector mixing, and ell sensitivity showing a sweet spot near $\ell\sim1$.
These results do not solve the eternal-inflation measure problem, but demonstrate
a reproducible toy framework for testing locality-weighted measures against
global census baselines.
\end{abstract}

\maketitle

\input{sections/01_introduction}
\input{sections/02_background}
\input{sections/03_isr_framework}
\input{sections/04_toy_model}
\input{sections/05_experiments}
\input{sections/06_results}
\input{sections/07_discussion}
\input{sections/08_limitations}
\input{sections/09_conclusion}

\bibliographystyle{apsrev4-2}
\bibliography{bib/references}

\newpage
\appendix
\input{sections/10_appendix_simulation}
\input{sections/11_appendix_failures}
\input{sections/12_appendix_reproducibility}
\input{sections/13_appendix_degenerate}

\end{document}
