% Appendix C: Reproducibility
\section{Code and reproducibility}
\label{app:reproducibility}

The full codebase is available at
\url{https://github.com/jenholm/physics_models/tree/main/inflationary-sector-renormalization}.
All results in this paper were produced with the following software versions:

\begin{itemize}
  \item Commit \texttt{fb1b497} of this repository.
  \item Python 3.12.3 with: numpy 2.4.6, scipy 1.17.1, pandas 3.0.3,
        matplotlib 3.10.9, PyYAML 6.0.1.
  \item Config hashes: base.yaml \texttt{1fcc4c5c9ac7},
        landscapes.yaml \texttt{ef664ae36835}.
  \item A working \LaTeX\ distribution with revtex4-2, bibtex and
        standard packages.
\end{itemize}

\subsection{Running experiments}

\begin{verbatim}
git clone https://github.com/jenholm/physics_models.git
cd physics_models/inflationary-sector-renormalization
python -m venv .venv
source .venv/bin/activate
pip install -r requirements.txt
python -m compileall isr experiments
python run_all.py
\end{verbatim}

\subsection{Expected outputs}

The script \texttt{run\_all.py} runs all twelve experiments sequentially.
Key output files include:

\begin{itemize}
  \item \texttt{outputs/isr\_result\_summary.md} --- compiled Markdown report.
  \item \texttt{outputs/global\_measure\_vs\_cutoff.json} --- global census
        probabilities per cutoff.
  \item \texttt{outputs/isr\_measure\_vs\_cutoff.json} --- \ISR probabilities.
  \item \texttt{outputs/kernel\_comparison\_table.csv} --- cutoff stability
        by kernel.
  \item \texttt{outputs/stress\_test\_results.csv} --- all 100 stress-test runs.
  \item \texttt{outputs/stress\_test\_summary.json} --- aggregated stress metrics.
  \item \texttt{outputs/configuration\_space\_locality\_summary.csv} ---
        configuration-space locality diagnostics.
  \item \texttt{outputs/kernel\_weighted\_sector\_averaging.csv} ---
        kernel-weighted sector averaging.
  \item \texttt{outputs/ell\_sensitivity\_results.csv} --- ell scan (Exp~9).
  \item \texttt{outputs/ell\_sensitivity\_summary.json} --- aggregated ell metrics.
  \item \texttt{outputs/sigma\_ell\_boundary\_results.csv} --- sigma-by-ell grid (Exp~10).
  \item \texttt{outputs/sigma\_ell\_boundary\_summary.json} --- aggregated boundary metrics.
  \item \texttt{outputs/flat\_parent\_composition.json} --- composed-measure sanity check (Exp~11).
  \item \texttt{outputs/landscape\_perturbation\_results.json} --- perturbed-landscape robustness (Exp~12).
\end{itemize}

\subsection{Paper figures and tables}

Figures are generated by \texttt{paper/generate\_figures.py}.
Tables are generated by \texttt{paper/generate\_tables.py}.
The paper is built with \texttt{make} in the \texttt{paper/} directory.
